%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

 \cventry
    {~Vector Institute} % Institution
    {~Student Affiliate Researcher} % Degree
    {Toronto, Canada} % Location
    {June, 2023 - December, 2025} % Date(s)
    {~~~·~~~\scriptsize{Affiliated to the Vector Institute for Artificial Intelligence as a MASc student researcher.}\newline}
%---------------------------------------------------------
 \cventry
    {~Coleção.moda} % Institution
    {~Machine Learning Engineer} % Degree
    {Florianopolis, Brazil} % Location
    {October, 2022 - May, 2023} % Date(s)
    {~~~·~~~\scriptsize{Implemented Latent Diffusion models for text-to-image generation.}\newline
     ~~~·~~~~\scriptsize{Applied Data Science analysis concepts to consumer data.}\newline}
%---------------------------------------------------------
      \cventry
    {~Graduate Program of Computer Science~~~·~~~UFRGS~~~·~~~Advised by Prof. \href{https://scholar.google.com/citations?user=f2UrnmAAAAAJ&hl=pt-BR}{Manuel M. Oliveira}} % Institution
    {~Undergraduate Research Assistant} % Degree
    {Porto Alegre, Brazil} % Location
    {January, 2022 - October, 2022} % Date(s)
    {~~~·~~~\scriptsize{Performed research exploring latent space arithmetic in SyleGANs.}\newline
     ~~~·~~~~\scriptsize{Applied Generative Modeling and GAN Inversion concepts using TensorFlow and PyTorch.\newline}}
%---------------------------------------------------------
    \cventry
    {Pix Force: Computer Vision and  Image Processing} % Institution
    {Research Intern} % Degree
    {Porto Alegre, Brazil} % Location
    {January, 2022 - May, 2022} % Date(s)
    {~·~~~\scriptsize{Developed computer vision applications for sports performance monitoring.}\newline
     ~·~~~~\scriptsize{Improved object localization and segmentation algorithms based on concepts from scientific papers.\newline}}
%---------------------------------------------------------
  \cventry
    {Graduate Program of Computer Science~~~·~~~UFRGS~~~·~~~Advised by Prof. \href{https://scholar.google.com/citations?user=f2UrnmAAAAAJ&hl=pt-BR}{Manuel M. Oliveira}} % Institution
    {Undergraduate Research Assistant} % Degree
    {Porto Alegre, Brazil} % Location
    {July, 2021 - January, 2022} % Date(s)
    {~·~~~\scriptsize{Developed applications for the capturing step in low-light video enhancement pipelines for mobile devices.}\newline
     ~·~~~\scriptsize{Utilized the Camera2 API in Android Studio to implement low-light video recording functions.\newline}}
%---------------------------------------------------------
  \cventry
    {Graduate Program of Microelectronics~~~·~~~UFRGS~~~·~~~Advised by Profs. \href{https://scholar.google.com/citations?hl=pt-BR&user=emFRxDUAAAAJ}{Sergio Bampi} and \href{https://scholar.google.com/citations?hl=pt-BR&user=V9ZSEjoAAAAJ}{Mateus Grellert}} % Institution
    {Undergraduate Research Assistant} % Degree
    {Porto Alegre, Brazil} % Location
    {July, 2018 - December, 2021} % Date(s)
    {~·~~~\scriptsize{Performed research in diverse subjects such as IC design, video coding, and learning-based image compression.}\newline
     ~·~~~~\scriptsize{Developed dedicated hardware arithmetic operators for computational intensive video coding operations.}\newline
     ~·~~~~\scriptsize{Evaluated perceptual metrics' impact in the inter-frame motion estimation module of the HEVC video coding standard.}\newline
     ~·~~~~\scriptsize{Assessed the rate-distortion-complexity tradeoff present in learning-based image compression models.}
    }

\end{cventries}